### 2016-06-26 sec6_experiment.tex
A more complete one
hhah

\section{Experimental Study}
\label{sec:exp}
In this section, we present our experimental findings on
deploying our GCMP detectors to large-scaled real trajectories.
All the experiments are carried out on our in-house cluster: Dianwei. The cluster includes 12 nodes, each of which is equipped with four quad-core 2.2GHz Intel processors, 32 GB memory and gigabit Ethernet. The cluster is installed with CentOS 5.5. operating system.

\textbf{Environment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}
to manage our cluster. One node is dedicated as Yarn's master node, and each other node reserves one core and 2 GB memory for
Yarn processes. We use Apache Spark 1.5.5~\cite{zaharia2012resilient} as the MapReduce framework. Spark takes
the remaining 11 nodes as the computing nodes.
To fully utilize the computing power of the cluster, 
we assign each node to run five executors, each executor takes three cores and 5 GB memory. We use "yarn-cluster" mode
for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
at the same time. We use HDFS as our storage engine with replicator factor of 1.
The summary of the configuration is as in the following table:

\begin{table} [h]
\centering
\begin{tabular}{|l|c|}
\hline 
Parameter & Value  \\ 
\hline 
Java Version & 1.7.0 \\ 
\hline 
Spark Version & 1.5.5 \\ 
\hline 
spark.driver.memory & 2GB \\ 
\hline 
spark.executor.cores & 3  \\ 
\hline 
spark.executor.instances & 54 \\ 
\hline 
spark.executor.memory & 5GB \\ 
\hline 
spark.master & yarn-cluster \\
\hline 
spark.serializer & KryoSerializer \\ 
\hline 
\end{tabular} 
\end{table}

\textbf{Datasets}: We prepare three real datasets for experiments. The details of the datasets are as follows:
\begin{itemize}
\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}: this dataset collects 
18,670 trajectories for passengers in Beijing over three years. The data are collected
per around 5 seconds. Each data point records a trajectory ID and the latitude/longitude information.
\item{Shopping}~\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}: this dataset contains
 visitors trajectories in ATC shopping center in Osaka. The samples are taken per
 around 0.5 seconds. There are in total 13,183 trajectories. Each data point is a 
 trajectory ID with in-door coordinates.
\item{Taxi}: this dataset records 15,054 Singapore taxi trajectories over one month span. The sample 
rate is around 30 seconds. Each data point is the taxi plate with latitude/longitude information.
\end{itemize}

\textbf{Preprocessing}: We replace timestamps with global sequences for each dataset. The sequence number
$0$ is the earliest timestamp among all trajectories in a dataset. We use the sampling rate of 
each dataset as the tick of the sequence number and every data point is mapped to the nearest ticks. If
several points mapped to the same tick, they are merged by averaging the location coordinates.
For missing data within small intervals (i.e., sequence difference less than 10), 
we use linear interpolation to fill them. 
We then use DBSCAN ($\epsilon=5, minPt=10$ for GeoLife and Shopping, $\epsilon=20, minPt=10$ for Taxi)
as the clustering algorithm for preprocessing.  
Note that both our TRPM and SPARE algorithms treat the preprocessing as a black box and other
spatial clustering methods are also applicable. The clustered snapshots are stored in HDFS in $\langle t, S_t \rangle$ pair, where
$t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
After preprocessing, the statistics of the three datasets are presented in Table~\ref{exp:dataset}.

\begin{table} [h]
\center
\small
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{ACTShopping} &  \textbf{Geolife} &  \textbf{SingTaxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
\# average ts & 3,114  & 2,924 & 19,667 \\ 
\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
%\# of patterns & 3,741 & 4,369  & 7,585 \\
%\hline
\end{tabular}
\caption{Statistics of data set}
\label{exp:dataset}
\end{table}

\textbf{Parameters}: To systematically study the performance of
our algorithms, we conduct experiments on various conditions. The variables
to be tested and their value ranges are listed in Table~\ref{tbl:parameters}. 
Default values are highlighted in bold.
\begin{table}[h]
\small
\begin{tabular}{c|l|l}
\hline 
\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
N & number of executors & 1, 14, 24, 34, 44, \textbf{54}\\ 
\hline 
\end{tabular} 
\caption{Variables and their default values}
\label{tbl:parameters}
\end{table}

\textbf{Number of patterns under different parameters}: We first 
analyze the number of patterns exist in each dataset under different conditions. The results are presented in Figures~\ref{exp:patterns_vary}. As expected, the number of patterns differs under in different scenarios. Larger $M$, $L$, $K$ imply smaller number of patterns, because lesser patterns are able to meet stricter $M$, $L$, $K$ constraints. In contrast, larger $G$ implies larger number of patterns. This is because larger gaps relaxes the pattern constraint. Two interesting observations are made on $L$ and $G$.
First, as $L$ increases from $10$ to $20$, the number of patterns drops quickly (50\% less). Second, opposed to $L$'s trend, as $G$ reaches to $30$ from $25$, the number of patterns bursts (near 50\% more). The distribution of patterns under $G$ and $L$ reveals that there are many companions in real life which are short and intermittent. With GCMP, we can discover these patterns by adjusting property $L$ and $G$s.

\begin{figure}[h]
\centering
 	 \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
        \caption{Number of patterns vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
        \caption{Number of patterns vary $K$}
    \end{subfigure}  
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
        \caption{Number of patterns vary $L$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
        \caption{Number of patterns vary $G$}
    \end{subfigure}    
\caption{Number of patterns discovered from real datasets}
\label{exp:patterns_vary}
\end{figure}

\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study. TRPM and SPARE are implement as described in Section 4 and 5. SPARE-LB extends SPARE by appending an additional load balance stage to the map phase. 
When the mappers complete, SPARE-LB collects the size of stars from all mappers. 
Then a best-fit strategy is applied for task allocation. In best-fit, 
tasks are assigned in decreasing order of their sizes, and the most costly
unassigned task is allocated to the current mostly empty reducer. 
In SPARE-LB, we simply use the number of edges in stars as a cost estimation. The other
part of SPARE-LB is identical with SPARE.

%\subsection{Effects of $G$ on GCMP}
%\begin{figure*}[t]
%\centering
%    \begin{subfigure}[b]{0.3\textwidth}
%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_geolife.eps}
%        \caption{Geolife}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.33\textwidth}
%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_shopping.eps}
%        \caption{ACTShopping}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.3\textwidth}
%        \includegraphics[width=\textwidth]{exp/effectiveness/effect_taxi.eps}
%        \caption{SingTaxi}
%    \end{subfigure}
%\caption{Effectiveness of GCMP model on sampled datasets.}
%\label{exp:effectiveness}
%\end{figure*}
%We first study the effects of introducing gap parameter $G$ on pattern discovery.
%As shown in Figure~\ref{fig:related_work_scalability},
%existing works are not able to handle large trajectories, 
%we sample and cluster $1$ million trajectory points from the three real data.
%We use two instances of GCMPs, GCMP-L where the $L$ value is default and GCMP where $L = 1$.  We measure the number
%of patterns discvoered by different methods. The results are presented in Figure~\ref{exp:effectiveness}.
%
%We can see from Figures~\ref{exp:effectiveness} that the number of patterns
%discovered by GCMP is positively related to $G$. When $G =1$, the number
%of patterns returned by GCMP and GCMP-L are identical to \emph{convoy}. As $G$ grows,
%the number returned by GCMP-L converges to \emph{platoon}. For example, in (a), two
%patterns converge when $G$ is $40$. Similarly in (b) and (c), two patterns converge
%when $G$ is $50$. The reason is that when $G$ is large enough,
% all \emph{platoon}s are $G$-connected. Similar
% trend applies between GCMP and \emph{swarm}. As see from the figures, in (a), two
% patterns converge at $G=50$; while in (b) and (c) the two patterns converge
% at $G=60$ and $G=40$ respectively. We further
% note that, existing patterns has different granularity in temporal domain. As we seen
% from the three figures, the number of \emph{swarm} is greater than \emph{platoon} and
% \emph{convoy}. Despite none of the existing patterns are able to fine-grain control
% the temporal domain of patterns, GCMP can discover the patterns more precisely. 
% These results confirms the usefulness of GCMP in expressing other patterns.
%  
%

\subsection{Performance Comparison}
Since the both TRPM and SPARE utilizes pruning rules that related to the pattern parameters $M$,$K$,$L$,$G$. It is interesting to
see their performances under different settings.
We run the three algorithms using all three datasets 
and report their overall performances in Figures~\ref{exp:performance_vary}.
In brief, all of the three algorithms 
are able to handle the large-scaled real
datasets. However, SPARE algorithms are obviously more efficient than TRPM. 
In the case when $G$ is large (i.e., $G=30$), 
TRMP takes near three hours for Taxi dataset, which is 15 times slower than SPARE algorithms. Besides, SPARE-LB is consistently more efficient than SPARE, with an average of 20\% improvements.
Another general observation
is that all of the three algorithms run slower in the Taxi dataset as compared to
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset.
 In summary, SPARE outperforms TRMP in all cases. Next, we analyze the details of each experiments.

\begin{figure*}[t]
\centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
        \caption{Shopping vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
        \caption{Shopping vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
        \caption{Shopping vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
        \caption{Shopping vary $G$}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}       
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}
%\subsubsection{Effects of pattern parameters M,L,K,G}
\textbf{Vary $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
present the performance when $M$ changes.
As the figures show, SPARE based algorithms runs much faster than TRPM. We can see that SPARE
speeds up TRPM 2.7 times in Shopping data, 3.1 times in Geolife data and
7 times in Taxi data. An interesting observation is that, the running times
of all algorithms slightly decrease as $M$ grows. This is
because when $M$ becomes bigger, smaller clusters or stars can be directly pruned, which brings in the efficiency.

\textbf{Vary $K$}: Figure~\ref{exp:performance_vary} (b),(f),(j) 
presents the performances when $K$ changes. 
There are two interesting findings. 
First, SPARE based algorithms and TRPM takes different trends as $K$ increases. 
When $K$ increases, SPARE and SPARE-LB tends to run faster
while TRPM continuously slows down. For SPARE, the trends are resulted from more pruning powers brought
by $K$. When $K$ increases, more sequences can be pruned by the \emph{sequence simplification}.
Conversely, TRPM fails to utilize $K$ for pruning. Moreover, as $K$ increases, $\eta$ in TRPM grows, indicating more replication of snapshots. 
This explains the low performance of TRPM.  Second, when $K$ is small (i.e, $K$=120), TRPM could outperform SPARE. This is because smaller $K$ indicates small partition size in TRPM but restricted the pruning power in SPARE. As a result, TRPM wins 10\% in Geolife dataset. However, by leveraging the load balancing, SPARE-LB is still faster than TRPM.

\textbf{Vary $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) presents the performances when $L$ changes. We can see that SPARE based algorithms are still superior than TRPM, where SPARE-LB outperforms TRPM near 10 times when $L =10$.
An interesting observation is that $L$
provides good pruning power from $10$ to $20$ for both TRPM and SPARE based algorithms. The major reason is that the decrease of $L$ invalidates many candidates (as shown in Figure~\ref{exp:patterns_vary} (c)), thus the prunings in both SPARE and TRPM become more significant.  As $L$ continues to increase, we can see that TRPM's performance gain is larger than SPARE based algorithms. This is because larger $L$ indicates smaller $\eta$, which is more beneficial to TRPM.

\textbf{Vary $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) presents the performances when $G$ changes.  Unlike other cases, when $G$ increases, both TRPM and SPARE based algorithms run slower. The reason is that large $G$ relaxes the constraint of a pattern, thus the pruning powers of TRPM and SPARE is more restricted. We observe that there is a burst in performance of TRPM when $G$ reach to $30$. The major reason is that when $G$ becomes to 30, the number of valid patterns almost doubles as shown in Figure~\ref{exp:patterns_vary} (d). This indicate that during TRPM's line sweep, very few patterns can be pruned, making the candidate set grows exponentially. Similarly, SPARE algorithms are also affected by the increase of $G$. However we do not observe such a burst for SPARE. The reason is bi-folded. First, SPARE can utilize $K$, $L$ to retain the power of pruning. Second, SPARE leverages \emph{forward closure check} to quickly output valid patterns and avoids to enumerating many candidates.
%
%
% However, since SPARE algorithms are able to utilize $K$, $L$, $M$ in pruning, the 
%
%
%In general, both TRPM and SPARE
%runs slower when $G$ increases. This is because, when $G$ increases, exponentially more valid patterns
%exist. In other words, the pruning powers in TRPM and SPARE become weaker. We notice
%that there is an burst of TRPM as $G$ increases. The major reason is that 
%during line-sweep, if $G$-increases, each candidate needs to wait for more time before expiring.
%This makes the candidate set exponentially grows and 
%the join operation becomes very expensive.
%Unlike TRPM, SPARE is although affected by the increase of $G$, 
%but the impact is marginal as compared
%to TRPM. This is because, although true patterns may become 
%exponentially large as $G$ increases, the \emph{forward closure check} of SPARE
%can quickly output true patterns without enumerating every of its subset.
%\subsubsection{Effects of clusters $\epsilon$, minPt}

%\subsubsection{Anatomy of SPARE and TRPM}

\subsection{Analysis of SPARE and SPARE-LB}
As SPARE based algorithms are superior than TRPM,
we further analyze several more aspects of SPARE namely, \emph{power of pruning}, \emph{load balance} and \emph{scalability}.

\subsubsection{Power of sequence simplification}
One of the core techniques used in SPARE is the \emph{sequence simplification} (see Section 5.2.1). 
As shown in  Algorithm~\ref{algo:apriori_mining}, we use $\mathtt{sim}(T)$
to prune false candidates. To study the power of sequence simplification,
we collect the total number of pairs that are pruned before apriori enumeration. The
statistics are shown in Table~\ref{tbl:pruning} under default parameters. The result states that the \emph{sequence simplification} is a very powerful pruning technique. It cuts off near 90\% of the initial pairs, which significantly reduces the costs
of later enumerations. This confirms the necessity and usefulness of design such a technique.

>>>>

\section{Experimental Study}
\label{sec:exp}
In this section, we evaluate the efficiency and scalability of our proposed distributed GCMP detectors on real trajectory datasets. All the experiments are carried out in a cluster with $12$ nodes, each equipped with four quad-core $2.2$GHz Intel processors, $32$GB memory and gigabit Ethernet. 
%The cluster is installed with CentOS 5.5. operating system.

\textbf{Environment Setup}: We use Yarn\footnote{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html} to manage our cluster. We pick one machine as the Yarn's master node, and the remainings reserve one core and $2$GB memory for Yarn processes. We deployed our GCMP detector on Apache Spark 1.5.5~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory. In Spark, one of the $55$ executor is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
All our implementations as well as cluster setups are open-sourced in XXX.
%can be referred in our 
%We use ``yarn-cluster'' mode
%for Spark which randomly picks one executor to act as the Application Master. Such a configuration allows us to run 162 tasks
%at the same time. We use HDFS as our storage engine with replicator factor of 1.
%The summary of the configuration is as in the following table:

\eat{
\begin{table} [h]
\centering
\begin{tabular}{|l|c|}
\hline 
Parameter & Value  \\ 
\hline 
Java Version & 1.7.0 \\ 
\hline 
Spark Version & 1.5.5 \\ 
\hline 
spark.driver.memory & 2GB \\ 
\hline 
spark.executor.cores & 3  \\ 
\hline 
spark.executor.instances & 54 \\ 
\hline 
spark.executor.memory & 5GB \\ 
\hline 
spark.master & yarn-cluster \\
\hline 
spark.serializer & KryoSerializer \\ 
\hline 
\end{tabular} 
\end{table}
}

\textbf{Datasets}: We use three real trajectory datasets in different application scenarios:
\begin{itemize}
\item{Geolife}~\footnote{http://research.microsoft.com/en-us/projects/geolife/}. The dataset essentially keeps all the travel records of 182 users for a period
of over three years, including multiple kinds of transportation modes (walking, driving and taking public
transportation). For each user, the GPS information is collected periodically and 91 percent of the trajectories
are sampled every 1 to 5 seconds.
\item{Shopping}\footnote{http://www.irc.atr.jp/crest2010\_HRI/ATC\_dataset/}. The dataset contains
  trajectories of visitors in the ATC shopping center in Osaka. To better capture the indoor activities, the visitor locations are sampled every half second, resulting in $13,183$ long trajectories. 
\item{Taxi}. The dataset tracks the trajectories of $15,054$ taxies in Singapore over August 2008. The sampling
rate is around 30 seconds. 
\end{itemize}

\textbf{Preprocessing}: We replace timestamps with global sequences (starting from $1$) for each dataset. 
We set a fixed sampling rate for each dataset (i.e., Geolife = 5 seconds, Shopping=0.5 seconds, Taxi = 30 seconds)
and use linear interpolation to fill missing values.
%For each dataset, we set a fixed sampling rate (CLEARLY STATE THE SAMPLING RATE FOR EACH DATASET) and use linear interpolation to fill missing values. 
%Finally, we obtain a set of trajectories with equal length. 
%Finally, we obtain a set of dense trajectories with equal length. 
For the clustering method, we use DBSCAN~\cite{ester1996density} and customize its two parameters $\epsilon$ and $minPt$~\footnote{$\epsilon$ is the maximum neighborhood range to be concerned, $minPt$ is the minimum number of objects to form a dense region.}. We set $\epsilon=5$, $minPt=10$ for GeoLife and Shopping datasets; and $\epsilon=20$, $minPt=10$ for Taxi dataset. Note that other clustering methods and settings can also be applied. The clustered snapshots are stored in HDFS as $\langle t, S_t \rangle$ pair, where $t$ is the timestamp, $S_t$ contains the clusters at snapshot $t$. 
After preprocessing, the statistics of the three datasets are presented in Table~\ref{exp:dataset}.

\begin{table} [h]
\center
\small
\begin{tabular}{|l|l|l|l|}
\hline
 \textbf{Attributes}& \textbf{Shopping} &  \textbf{Geolife} &  \textbf{SingTaxi} \\ 
\hline 
\# objects  & 13,183 & 18,670 & 15,054\\ 
\hline
%\# average ts & 3,114  & 2,924 & 19,667 \\ 
%\hline
\# data points  & 41,052,242 & 54,594,696 & 296,075,837\\ 
\hline
\# snapshots  & 16,931 & 10,699 & 44,364\\ 
\hline
\# clusters  & 211,403  & 206,704& 536,804\\
\hline
avg. cluster size  & 171 & 223 & 484\\
\hline
%\# of patterns & 3,741 & 4,369  & 7,585 \\
%\hline
\end{tabular}
\caption{Statistics of data set}
\label{exp:dataset}
\end{table}

\textbf{Parameters}: To systematically study the performance of
our algorithms, we conduct experiments on various parameter settings. The parameters to be evaluated are listed in Table~\ref{tbl:parameters}, with default settings in bold. 
\begin{table}[h]
\small
\begin{tabular}{c|l|l}
\hline 
\textbf{Variables} & \textbf{Meaning} & \textbf{Values} \\ 
\hline 
M & min size of object set &  5, 10,  \textbf{15}, 20, 25 \\ 
\hline 
K & min duration & 120, 150, \textbf{180}, 210, 240 \\ 
\hline 
L & min local duration & 10, 20, \textbf{30}, 40,50 \\ 
\hline 
G & max gap & 10, 15, \textbf{20}, 25, 30 \\ 
\hline
$O_r$ & ratio of objects & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
$T_r$ & ratio of snapshots & 20\%,40\%, 60\%, 80\%, \textbf{100\%} \\ \hline
N & number of machines & 1, 3, 5, 7, 9, \textbf{11}\\ 
\hline 
\end{tabular} 
\caption{Variables and their default values}
\label{tbl:parameters}
\end{table}

\eat{
\textbf{Number of patterns under different parameters}: We first 
analyze the number of patterns exist in each dataset under different conditions. The results are presented in Figures~\ref{exp:patterns_vary}. As expected, the number of patterns differs under in different scenarios. Larger $M$, $L$, $K$ imply smaller number of patterns, because lesser patterns are able to meet stricter $M$, $L$, $K$ constraints. In contrast, larger $G$ implies larger number of patterns. This is because larger gaps relaxes the pattern constraint. Two interesting observations are made on $L$ and $G$.
First, as $L$ increases from $10$ to $20$, the number of patterns drops quickly (50\% less). Second, opposed to $L$'s trend, as $G$ reaches to $30$ from $25$, the number of patterns bursts (near 50\% more). The distribution of patterns under $G$ and $L$ reveals that there are many companions in real life which are short and intermittent. With GCMP, we can discover these patterns by properly adjusting $L$ and $G$s.

\begin{figure}[h]
\centering
 	 \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_M.eps}
        \caption{Number of patterns vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_K.eps}
        \caption{Number of patterns vary $K$}
    \end{subfigure}  
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_L.eps}
        \caption{Number of patterns vary $L$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/effectiveness/patterns_vary_G.eps}
        \caption{Number of patterns vary $G$}
    \end{subfigure}    
\caption{Number of patterns discovered from real datasets}
\label{exp:patterns_vary}
\end{figure}
}

\eat{
\textbf{Algorithms}: We implement TRPM, SPARE and SPARE-LB for comparison study. TRPM and SPARE are implement as described in Section 4 and 5. SPARE-LB extends SPARE by appending an additional load balance stage to the map phase. 
When the mappers complete, SPARE-LB collects the size of stars from all mappers. 
Then a best-fit strategy is applied for task allocation. In best-fit, 
tasks are assigned in decreasing order of their sizes, and the most costly
unassigned task is allocated to the current mostly empty reducer. 
In SPARE-LB, we simply use the number of edges in stars as a cost estimation. The remaining
parts of SPARE-LB are identical to SPARE.
}

\subsection{Performance Evaluation}
\eat{
Since the both TRPM and SPARE utilizes pruning rules that related to the pattern parameters $M$,$K$,$L$,$G$. It is interesting to
see their performances under different settings.
We run the three algorithms using all three datasets 
and report their overall performances in Figures~\ref{exp:performance_vary}.
In brief, all of the three algorithms 
are able to handle the large-scaled real
datasets. However, SPARE algorithms are obviously more efficient than TRPM. 
In the case when $G$ is large (i.e., $G=30$), 
TRMP takes near three hours for Taxi dataset, which is 15 times slower than SPARE algorithms. Besides, SPARE-LB is consistently more efficient than SPARE, with an average of 20\% improvements.
Another general observation
is that all of the three algorithms run slower in the Taxi dataset as compared to
other two datasets. This is because Taxi dataset contains
the most number of temporal data points, which is around 7 times of Shopping
dataset and 5 times of geolife dataset.
 In summary, SPARE outperforms TRMP in all cases. Next, we analyze the details of each experiments.
}
\begin{figure*}[t]
\centering
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_M.eps}
        \caption{Shopping vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_K.eps}
        \caption{Shopping vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_L.eps}
        \caption{Shopping vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_G.eps}
        \caption{Shopping vary $G$}
    \end{subfigure}

@@

    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_M.eps}
        \caption{Taxi vary $M$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_K.eps}
        \caption{Taxi vary $K$}
    \end{subfigure}
    \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_L.eps}
        \caption{Taxi vary $L$}
    \end{subfigure}
       \begin{subfigure}[b]{0.23\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_G.eps}
        \caption{Taxi vary $G$}
    \end{subfigure}       
\caption{Performance of SPARE and TRPM on real datasets under different pattern parameters.}
\label{exp:performance_vary}
\end{figure*}
%\subsubsection{Effects of pattern parameters M,L,K,G}
\textbf{Varying $M$}: Figures~\ref{exp:performance_vary} (a),(e),(i)
present the performance with increasing $M$. The SPARE framework demonstrates a clear superiority over TRPM framework, with a boosting factor of  $2.7$ times in Shopping, $3.1$ times in Geolife and
$7$ times in Taxi. As $M$ increases, the running time of both frameworks slightly improves because the number of clusters in each snapshot drops, generating fewer valid candidates.

\textbf{Varying $K$}: The performance with increasing $K$ is shown in Figure~\ref{exp:performance_vary} (b),(f),(j).  SPARE tends to run faster, whereas the performance of TRPM degrades dramatically. This is caused by the \emph{sequence simplification} procedure in SPARE, which can prune many candidates with large $K$. However, the line sweep algorithm in TRPM does not utilize such property for pruning. It takes longer time because more replication data has to be handled in each partition.

%Second, when $K$ is very small (i.e, $K=0.XXX|T|$), TRPM could outperform SPARE because smaller $K$ indicates small partition size in TRPM but restricted the pruning power in SPARE. As a result, TRPM wins 10\% in Geolife dataset. However, by leveraging the load balancing, SPARE-LB is still faster than TRPM.

\textbf{Varying $L$}: Figures~\ref{exp:performance_vary} (c)(g)(k) present the performances with varying $L$. When $L=10$, SPARE can outperform TRPM by around $10$ times. We also observe that there is a significant performance improvement for TPRM when $L$ increases from $10$ to $20$ and later the running time drops smoothly. 
This is because $\eta$ is proportional to $O(L + 1/L)$. When $L$ is small (i.e., from $10$ to $20$),
$\eta$ decreases quickly (i.e., 30\%). As $L$ further increases (e.g, from $20$ to $30$),
$\eta$ decreases steadily (e.g, 15\%).
%CAN YOU EXPLAIN THIS FROM THE RELATIONSHIP between $\eta$ and $L$.

\eat{
An interesting observation is that $L$
provides good pruning power from $10$ to $20$ for both TRPM and SPARE based algorithms. The major reason is that the decrease of $L$ invalidates many candidates (as shown in Figure~\ref{exp:patterns_vary} (c)), thus the prunings in both SPARE and TRPM become more significant.

 As $L$ continues to increase, we can see that TRPM's performance gain is larger than SPARE based algorithms. This is because larger $L$ indicates smaller $\eta$, which is more beneficial to TRPM.
}

\textbf{Varying $G$}: Figures~\ref{exp:performance_vary} (d)(h)(l) present the performances with increasing $G$.  TRPM is rather sensitive to $G$. When $G$ is relaxed to larger values, more valid patterns would generate. TPRM has to set a higher replication factor and its running time degrades drastically when $G$ increases from $20$ to $30$. In contrast, with much more effective pruning strategy, our SPARE scales very well with $G$.

\eat{
We can see that both TRPM and SPARE run slower. The reason is that large $G$ relaxes the constraint of a pattern, thus the pruning powers of TRPM and SPARE is more restricted. We observe that there is a burst in performance of TRPM when $G$ reach to $30$. The major reason is that when $G$ becomes to 30, the number of valid patterns almost doubles as shown in Figure~\ref{exp:patterns_vary} (d). This indicate that during TRPM's line sweep, very few patterns can be pruned, making the candidate set grows exponentially. Similarly, SPARE algorithms are also affected by the increase of $G$. However we do not observe such a burst for SPARE. The reason is bi-folded. First, SPARE can utilize $K$, $L$ to retain the power of pruning. Second, SPARE leverages \emph{forward closure check} to quickly output valid patterns and avoids to enumerating many candidates.
}
\textbf{Varying $O_r$}: Figures~\ref{exp:performance_vary_OT} (a)(b)(c) present 
the performances wrt. increasing number of total objects. The x-axis are the ratio
of objects sampled from the corresponding datasets. We can see that the performance of
both TRPM and SPARE decreases linearly to the the number of total objects. This
is reasonable since larger $O_r$ results in more clusters per snapshot, which affects
the line-sweep in TRPM and the aggregate graph in SPARE. However in all cases, SPARE
consistently outperforms TRPM.

\textbf{Varying $T_r$}: Figures~\ref{exp:performance_vary_OT} (d)(e)(f) present 
the performances wrt. increasing number of total snapshots.  The x-axis represents the size of
snapshots sampled from the corresponding datasets. We again observe the linear decrease of
the performances wrt. the number of snapshots. In all cases, SPARE is faster than
TRPM. We further observe that as $T_r$ grows, the gaps between SPARE and TRPM tends
to be larger, this is because larger $T_r$ results larger partition size, and more 
snapshots needs to be swept in TRPM.

\begin{figure}[h]
\centering
	\begin{subfigure}[b]{0.22\textwidth}
	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
        \caption{Shopping vary $O_r$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
        \caption{Geolife vary $O_r$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
        \caption{Taxi vary $O_r$}
    \end{subfigure}
    \begin{subfigure}[b]{0.22\textwidth}
	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
        \caption{Shopping vary $T_r$}
    \end{subfigure}
 	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
        \caption{Geolife vary $T_r$}
    \end{subfigure}
    	 \begin{subfigure}[b]{0.22\textwidth}
        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
        \caption{Taxi vary $T_r$}
    \end{subfigure}
 \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
 \label{exp:performance_vary_OT}
\end{figure}

\subsection{Analysis of SPARE framework}
In this part, we extensively evaluate the advantage brought by 
sequence simplification and load balancing techniques.
